Joint Satellite Distributions in the Local Group

### 2017-10-02 paper/paper.tex
+1 paragraph distributions

@@

We compare the two satellite distributions by always keeping the same
number of satellites around each galaxy.
This means that the magnitude cut corresponding to the faintest
satellite included in the sample is different in each case.
We make this choice for two reasons. 
First to always be sure that there is a non-zero number of satellites to make the computations. 
Second, to be able to compare the two halos at a fixed number of
satellites.

>>>>

\subsection{Parameter Distributions}

We charaterize the $\mu$ distribution by a power law probability
density distribution
\begin{equation}
P(\mu) = \frac{1}{\alpha}\mu^{\alpha-1}.
\end{equation}
We estimate the $\alpha$ using a bayesian approach, such as that
the likelihood of being $\alpha$ the power value given the observed values of $\{\mu_i\}$
  can be written as:

\begin{equation}
\mathcal{L}(\alpha|\{\mu_i\})=\frac{1}{Z_\alpha}\prod_{i=1}^{N_s}
\frac{1}{\alpha}\mu_i^{\alpha-1}, 
\end{equation}
%
where $Z_{\alpha}$ is a constant such as $\int_{0}^{\infty}
{\mathcal L}(\alpha|\{\mu_i\}) {\rm d}\alpha=1$. 
We report as $\hat{\alpha}$ the value of $\alpha$ 
maximizing the likelihood,

We characterize the distributions for the plane width and axis ratio
$b/a$, $b/c$ through a gaussian
\begin{equation}
P(x)  = \frac{1}{\sqrt{2\pi \sigma^2}} \exp{\left[-\frac{1}{2}\left(\frac{x-x_m}{\sigma}\right)^2\right]}
\end{equation}
In this case the maximum likelihood values for the parameter estimates
$\hat{x_m}$ and $\hat{\sigma}$ correspond to the mean and standard
deviation, respectively.

We summarize the results from the Illustris simulation by reporting
the maximum likelihood parameter estimates. 
In turn we use this us to estimate the probability of finding the
observed values in the Local Group and compare it against the highest
probabilty values.

@@

We compare the satellite distributions in the MW and M31 at fixed
satellite number.
This means that the magnitude cut corresponding to the faintest
satellite included in the sample is different in each case.
We make this choice for two reasons. 
First to always be sure that there is a non-zero number of satellites to make the computations. 
Second, to be able to compare the two halos at a fixed number of
satellites.
